A Blockchain Consensus Protocol With\\Horizontal Scalability

### 2018-04-24 conference-presentation/presentation.tex
Remove fairness
Clean up presentation

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage{calc}
\usepackage[absolute,overlay]{textpos}
\usepackage{graphicx}
\graphicspath{{./figures/}{../figures/}}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{comment}
\usepackage{MnSymbol,wasysym}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm}
\usepackage{makecell}
\usepackage[style=ieee]{biblatex}
\addbibresource{references.bib}

% https://tex.stackexchange.com/questions/124256/how-do-i-get-numbered-entries-in-a-beamer-bibliography
\setbeamertemplate{bibliography item}{\insertbiblabel}

@@

\setbeameroption{show notes}

@@

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}
\subsection{The dangers of centralisation}
\begin{frame}{The dangers of centralisation}
  \begin{itemize}
    \item Technological advancements give us convenience
    \item But it puts central authorities in control
    \item Most are motivated exclusively by profit
    \item Not always in the interest of the ``users''\footnote{Typically users of some free service X are, in fact, used by X.}
  \end{itemize}
\end{frame}

% \begin{frame}{The dangers of centralisation:~Examples}
%   \begin{itemize}
%     \item Facebook can predict your opinions and desires from your ``likes''~\cite{youyou2015computer},
%       and then create a ``psychographic'' profile for use in political campaigns~\cite{psychographic}
%     \item Baidu's promoted search result on medical care caused death of a student~\cite{weizexi}
%   \end{itemize}
%   \note{
%     \begin{itemize}
%       \item The treatment was phased out at clinical stage in the US because the success rate is too low
%       \item ``The study was conducted on 86,220 volunteers who have a Facebook account and who
%       completed a hundred-item personality questionnaire. The Facebook algorithm predicted the volunteers'
%       answers based on monitoring their Facebook Likes – which webpages, images and clips they tagged with the
%       Like button. The more Likes, the more accurate the predictions. The algorithm's predictions were compared
%       with those of work colleagues, friends, family members and spouses. Amazingly, the algorithm needed a set
%       of only ten Likes in order to outperform the predictions of work colleagues. It needed seventy Likes to
%       outperform friends, 150 Likes to outperform family members and 300 Likes to outperform spouses. In other
%       words, if you happen to have clicked 300 Likes on your Facebook account, the Facebook algorithm can
%       predict your opinions and desires better than your husband or wife!'' -Harari, \emph{Homo Deus}
%       \item The student had cancer---(synovial sarcoma)
%       \item Summary: we live in an age where companies and governments are able to control our thoughts,
%       where is the freedom and liberty in that?
%     \end{itemize}
%   }
% \end{frame}

@@

\subsection{Related work}
\begin{frame}{Related work}
    \begin{itemize}
        \item Off-chain solution
            \begin{itemize}
                \item Lightning Network
                \item Perun
            \end{itemize}
        \item On-chain solution
            \begin{itemize}
                \item Parameter tuning
                \item BFT consensus (e.g. Tendermint, ByzCoin)
                \item Sharding (e.g. Elastico, OmniLedger)
            \end{itemize}
    \end{itemize}
\end{frame}

@@

\begin{frame}{\subsecname}
  \begin{itemize}
    \item Goal 1: reach consensus on a collection of CP blocks amongst all the nodes
    \item Goal 2: create new CP blocks at the end of the protocol
    \item Uses an existing fault-tolerant consensus algorithm (HoneyBadgerBFT~\cite{miller2016honey}) as the building block
    \item But it cannot be used in a large network due to high communication complexity
    \item We overcome this limitation by selecting a small number of \emph{facilitators} from the network to run HoneyBadgerBFT
  \end{itemize}
\end{frame}

@@

\begin{frame}{\subsecname:~properties}
\label{def:consensus}
\begin{itemize}
    \item \emph{Agreement}:
        Every correct outputs the same set of facilitators.
    \item \emph{Validity}:
      The consensus result is valid such that a new set of facilitators can be computed from it.
    \item \emph{Fairness}:
        Every node with a CP block in the consensus result should have an equal probability of becoming a facilitator.
    \item \emph{Termination}:
        Every correct node eventually outputs a set of facilitators.
\end{itemize}
\end{frame}

@@

\section{Experimental results}
\begin{frame}{Implementation and experiment setup}
  \begin{itemize}
    \item Free and open source implementation on Github:
      \url{https://github.com/kc1212/checo}
    \item SHA256 for hash functions and Ed25519 for digital signature
    \item Experiment on the DAS-5\footnote{\url{http://www.cs.vu.nl/das5/}}
    \item Up to 1500 nodes
  \end{itemize}
\end{frame}

@@

\begin{frame}{Bibliography}
\printbibliography
\end{frame}

@@

\begin{frame}[noframenumbering]{Background on ACS}
  \begin{itemize}
    \item Asynchronous common subset
    \item A simplification of HoneyBadgerBFT~\cite{miller2016honey}
    \item $n$ nodes
    \item $t$ nodes may be malicious
    \item Input: every node proposes a set of values, e.g., $\{A, B\}, \{B, C\}, \dots$
    \item Output: set union of the majority, e.g., $\{A, B, C, \dots \}$
  \end{itemize}
\end{frame}

>>>>

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage{calc}
\usepackage[absolute,overlay]{textpos}
\usepackage{graphicx}
\graphicspath{{../presentation/figures/}{../figures/}}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{comment}
\usepackage{MnSymbol,wasysym}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm}
\usepackage{makecell}
\usepackage[style=ieee]{biblatex}
% \addbibresource{references.bib}

% https://tex.stackexchange.com/questions/124256/how-do-i-get-numbered-entries-in-a-beamer-bibliography
% \setbeamertemplate{bibliography item}{\insertbiblabel}

@@

% \setbeameroption{show notes}

@@

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}
\subsection{The dangers of centralisation}
\begin{frame}{The dangers of centralisation}
  \begin{itemize}
    \item Technological advancements give us convenience
    \item But it puts central authorities in control
    \item Many are motivated by profit or the goals of the local government
    \item The interest of the authorities do not align with the users
  \end{itemize}
\end{frame}

@@

\subsection{Related work}
\begin{frame}{Related work}
    \begin{itemize}
        \item Off-chain solution
            \begin{itemize}
                \item Lightning Network\footnote{\url{https://lightning.network/}}
                \item Perun\footnote{\url{https://perun.network}}
            \end{itemize}
        \item On-chain solution
            \begin{itemize}
                \item Parameter tuning
                \item BFT consensus (e.g. Tendermint\footnote{\url{https://www.tendermint.com/}}, ByzCoin\footnote{KJGKGF, USENIXSecurity16})
                \item Sharding (e.g. Elastico\footnote{LNZBGS, CCS16}, OmniLedger\footnote{KJGGSF, S\&P18})
            \end{itemize}
    \end{itemize}
\end{frame}

@@

\begin{frame}{\subsecname}
  \begin{itemize}
    \item Goal 1: reach consensus on a collection of CP blocks amongst all the nodes
    \item Goal 2: create new CP blocks at the end of the protocol
    \item Uses an existing fault-tolerant consensus algorithm (HoneyBadgerBFT\footnote{MXCSS, CCS16}) as the building block
    \item But it cannot be used in a large network due to high communication complexity
    \item We overcome this limitation by selecting a small number of \emph{facilitators} from the network to run HoneyBadgerBFT
  \end{itemize}
\end{frame}

@@

\begin{frame}{\subsecname:~properties}
\label{def:consensus}
\begin{itemize}
    \item \emph{Agreement}:
        Every correct outputs the same set of facilitators.
    \item \emph{Validity}:
      The consensus result is valid such that a new set of facilitators can be computed from it.
    % \item \emph{Fairness}:
    %     Every node with a CP block in the consensus result should have an equal probability of becoming a facilitator.
    \item \emph{Termination}:
        Every correct node eventually outputs a set of facilitators.
\end{itemize}
\end{frame}

@@

\section{Experimental results}
\begin{frame}{Implementation and experiment setup}
  \begin{itemize}
    \item Free and open source implementation on Github:
      \url{https://github.com/kc1212/checo}
    \item SHA256 for hash functions and Ed25519 for digital signature
    \item Experiment on the DAS-5\footnote{\url{http://www.cs.vu.nl/das5/}}
    \item Up to 1200 nodes
  \end{itemize}
\end{frame}

@@

% \begin{frame}{Bibliography}
% \printbibliography
% \end{frame}

@@

\begin{frame}[noframenumbering]{Background on ACS}
  \begin{itemize}
    \item Asynchronous common subset
    \item A simplification of HoneyBadgerBFT
    \item $n$ nodes
    \item $t$ nodes may be malicious
    \item Input: every node proposes a set of values, e.g., $\{A, B\}, \{B, C\}, \dots$
    \item Output: set union of the majority, e.g., $\{A, B, C, \dots \}$
  \end{itemize}
\end{frame}
